DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-06 manuscript/manuscript.Rmd
add caruana ref and add paper outline

---
title: "DeepTriangle: A Deep Learning Approach to Loss Reserving"
author:
  - name: Kevin Kuo
    affil: 1, *
    orcid: 0000-0001-7803-7901
affiliation:
  - num: 1
    address: Kasa AI
    email: kevin@kasa.ai
# firstnote to eighthnote
correspondence: |
  kevin@kasa.ai
journal: risks 
type: article
status: submit
bibliography: mybibfile.bib
abstract: |
   We propose a novel approach for loss reserving based on deep neural networks. The approach allows for joint modeling of paid losses and claims outstanding, and incorporation of heterogeneous inputs. We validate the models on loss reserving data across lines of business, and show that they improve on the predictive accuracy of existing stochastic methods. The models require minimal feature engineering and expert input, and can be automated to produce forecasts more frequently than manual workflows.
acknowledgement: |
  We thank Sigrid Keydana, Ronald Richman, and the volunteers on the Casualty Actuarial Society Committee on Reserves (CASCOR) who helped to improve the paper through helpful discussions.
conflictsofinterest: |
  The author declares no conflict of interest.
keywords: |
  loss reserving; machine learning; neural networks 
output: rticles::mdpi_article
---

@@

# Neural network preliminaries {#prelim}

@@

# Data and model architecture

@@

## Data source

We use the National Association of Insurance Commissioners (NAIC) Schedule P triangles [@meyers2011loss]. The dataset corresponds to claims from accident years 1988-1997, with development experience of 10 years for each accident year. In Schedule P data, the data is aggregated into accident year-development year records.

@@

## Training/testing setup

@@

## Response and predictor variables

@@

\begin{equation}
(Y_{i,1}, Y_{i,2}, \dots, Y_{i,j-1}).
\end{equation}
In other words, for each accident year and at each evaluation date for which we have data, we attempt to predict future development of the accident year's paid losses and claims outstanding based on the observed history as of that date. While we are ultimately interested in $P_{ij}$, the paid losses, we include claims outstanding as an auxiliary output of the model. Since the two quantities are related, we expect to obtain better performance by jointly training than predicting each quantity independently [@collobert2008unified].

@@

As shown in Figure \ref{fig:dt}, DeepTriangle is a multi-task network utilizing a sequence-to-sequence architecture [@sutskever2014sequence; @DBLP:journals/corr/SrivastavaMS15] with two prediction goals: claims outstanding and paid loss. We construct one model for each line of business and each model is trained on data from multiple companies.

@@

We utilize gated recurrent units (GRU) [@chung2014empirical], which is a type of recurrent neural network (RNN) building block that is appropriate for sequential data. A graphical representation of a GRU is shown in Figure \ref{fig:gru}, and the associated equations are as follows:

@@

@@

@@

## Deployment considerations

@@

Experiments
===========

## Evaluation metrics

@@

## Implementation and training

@@

We implement DeepTriangle using the keras R package [@chollet2017kerasR] with the TensorFlow [@tensorflow2015-whitepaper] backend. Code for producing the experiment results is available online.[^1]

@@

# Conclusion

We introduce DeepTriangle, a deep learning framework for forecasting paid losses. Our models are able to attain performance comparable, by our metrics, to modern stochastic reserving techniques without expert input. By utilizing neural networks, we can incorporate multiple heterogeneous inputs and train on multiple objectives simultaneously, and also allow customization of models based on available data.

>>>>

---
title: "DeepTriangle: A Deep Learning Approach to Loss Reserving"
author:
  - name: Kevin Kuo
    affil: 1, *
    orcid: 0000-0001-7803-7901
affiliation:
  - num: 1
    address: Kasa AI
    email: kevin@kasa.ai
# firstnote to eighthnote
correspondence: |
  kevin@kasa.ai
journal: risks 
type: article
status: submit
bibliography: mybibfile.bib
abstract: |
   We propose a novel approach for loss reserving based on deep neural networks. The approach allows for joint modeling of paid losses and claims outstanding, and incorporation of heterogeneous inputs. We validate the models on loss reserving data across lines of business, and show that they improve on the predictive accuracy of existing stochastic methods. The models require minimal feature engineering and expert input, and can be automated to produce forecasts more frequently than manual workflows.
acknowledgement: |
  We thank Sigrid Keydana, Ronald Richman, and the volunteers on the Casualty Actuarial Society Committee on Reserves (CASCOR) who helped to improve the paper through helpful discussions.
conflictsofinterest: |
  The author declares no conflict of interest.
keywords: |
  loss reserving; machine learning; neural networks 
output:
  bookdown::pdf_book:
    base_format: rticles::mdpi_article
---

@@

The rest of the paper is organized as follows: Section \@ref(prelim) provides a brief overview of neural network terminology, Section \@ref(data-arch) discusses the dataset used and introduces the proposed neural network architecture, Section \@ref(exps) defines the performance metrics we use to benchmark our models and discuss the results, and Section \@ref(conclusion) concludes.

# Neural Network Preliminaries {#prelim}

@@

# Data and Model Architecture {#data-arch}

@@

## Data Source

We use the National Association of Insurance Commissioners (NAIC) Schedule P triangles [@meyers2011loss]. The dataset corresponds to claims from accident years 1988-1997, with development experience of 10 years for each accident year. In Schedule P data, the data is aggregated into accident year-development year records. The procedure for constructing the dataset is detailed in @meyers2015stochastic.

@@

## Training/Testing Setup

@@

## Response and Predictor Variables

@@

\begin{equation}
(Y_{i,1}, Y_{i,2}, \dots, Y_{i,j-1}).
\end{equation}
In other words, for each accident year and at each evaluation date for which we have data, we attempt to predict future development of the accident year's paid losses and claims outstanding based on the observed history as of that date. While we are ultimately interested in $P_{ij}$, the paid losses, we include claims outstanding as an auxiliary output of the model. We elaborate on the reasoning behind this approach in the next section.

@@

As shown in Figure \ref{fig:dt}, DeepTriangle is a multi-task network utilizing a sequence-to-sequence architecture [@sutskever2014sequence; @DBLP:journals/corr/SrivastavaMS15] with two prediction goals: paid loss and claims outstanding. We construct one model for each line of business and each model is trained on data from multiple companies.

### Multi-task learning

Since the two target quantities, paid loss and claims outstanding, are related, we expect to obtain better performance by jointly training than predicting each quantity independently [@caruana1997multitask]. While @caruana1997multitask contains detailed discourse on the specific mechanisms of multi-task learning, we provide some heuristics on why it may improve predictions: by utilizing the reponse data from claims outstanding, we are effectively increasing the training data size since we are providing more signals to the learning algorithm; there may be hidden features, useful for predicting paid losses, that are more easily learned by trying to predict claims outstanding; also, by trying to predict claims outstanding during training, we are imposing a bias towards neural network weights which perform that task well, which lessens the likelihood of arriving at a model that overfits to random noise.

### Sequential input processing

@@

For handling the time series of paid losses and claims outstanding, we utilize gated recurrent units (GRU) [@chung2014empirical], which is a type of recurrent neural network (RNN) building block that is appropriate for sequential data. A graphical representation of a GRU is shown in Figure \ref{fig:gru}, and the associated equations are as follows:

@@

### Company Code Embeddings

@@

### Fully connected layers and outputs

@@

## Deployment Considerations

@@

# Experiments {#exps}

## Evaluation Metrics

@@

## Implementation and Training

@@

We implement DeepTriangle using the keras R package [@chollet2017kerasR] and TensorFlow [@tensorflow2015-whitepaper], which are open source software for developing neural network models. Code for producing the experiment results is available online.[^1]

@@

# Conclusion {#conclusion}

We introduce DeepTriangle, a deep learning framework for forecasting paid losses. Our models are able to attain performance comparable, by our metrics, to modern stochastic reserving techniques, without expert input. This means one can automate the model updating and report production at the desired frequency. By utilizing neural networks, we can incorporate multiple heterogeneous inputs and train on multiple objectives simultaneously, and also allow customization of models based on available data. To summarize, this framework maintains accuracy while providing  automatability and extensibility.
